Software Architectures to Integrate Workflow Engines in Science Gateways

### 2016-04-28 paper.tex
Closed note
Updates in cell colors in tables.

                                     & \cellcolor[HTML]{99D199}\textbf{11}

@@

  Specific interactions -- \texttt{R$_2$} & \cellcolor[HTML]{99EA99}2

@@

                                     & \cellcolor[HTML]{99C199}4

@@

  New engine type -- \texttt{E$_1$}  & \cellcolor[HTML]{99C499}3
                                     & \cellcolor[HTML]{99A799}4
                                     & \cellcolor[HTML]{99E199}2
                                     & \cellcolor[HTML]{99C499}3

@@

  \textbf{Total} (difficulty to extend) & \cellcolor[HTML]{99D199}\textbf{10}
                                     & \cellcolor[HTML]{99D199}\textbf{10}

@@

\caption{Architecture evaluation. Lower values (brighter colors) indicate better performance. On each row, metric values are
  normalized between 0 (best value) and 1 (worst value) to determine the
  color of the corresponding table cell. The normalized metric value $m'$ is
  defined as
  $\frac{m-m_{\mathrm{min}}}{m_{\mathrm{min}}-m_{\mathrm{max}}}$ where
  $m$ is the initial metric value, $m_{\mathrm{min}}$ and $m_{\mathrm{max}}$
  are the minimal and maximal values among all architectures. The RGB hexadecimal color code of the cell
  is \texttt{\#99XX99}, where X=F-4m'. \closednote{Tristan}{Use 6. Round to the nearest integer.}{Tristan}{Fixed.}}
\label{table:evaluation}
\end{table*}

@@

\paragraph{Robustness} The two workflow services are specific to
workflow execution (\texttt{R$_1$=2}). Interactions \texttt{b}
(counted twice), \texttt{c$_2$} (twice) and \texttt{d} (twice) also
are (\texttt{R$_2$=6}).
\note{Marc-e}{I understand both points. However, complexity is
  addressed in Robustness as well... I liked the idea of development effort. It's a tough call.}

@@

                                    & \cellcolor[HTML]{99D199}{0.44}

@@

  Extensibility (normalized total)  & \cellcolor[HTML]{99D199}{0.44}
                                     & \cellcolor[HTML]{99D199}{0.44}

@@

                                     & \cellcolor[HTML]{99DD99}{0.00}\\

@@

                                    & \cellcolor[HTML]{99EE99}\textbf{1.9}

>>>>

                                     & \cellcolor[HTML]{99D299}\textbf{11}

@@

  Specific interactions -- \texttt{R$_2$} & \cellcolor[HTML]{99EB99}2

@@

                                     & \cellcolor[HTML]{99C299}4

@@

  New engine type -- \texttt{E$_1$}  & \cellcolor[HTML]{99C599}3
                                     & \cellcolor[HTML]{99A899}4
                                     & \cellcolor[HTML]{99E299}2
                                     & \cellcolor[HTML]{99C599}3

@@

  \textbf{Total} (difficulty to extend) & \cellcolor[HTML]{99D299}\textbf{10}
                                     & \cellcolor[HTML]{99D299}\textbf{10}

@@

\caption{Architecture evaluation. Lower values (brighter colors) indicate better performance. On each row, metric values are
  normalized between 0 (best value) and 1 (worst value) to determine the
  color of the corresponding table cell. The normalized metric value $m'$ is
  defined as
  $\frac{m-m_{\mathrm{min}}}{m_{\mathrm{min}}-m_{\mathrm{max}}}$ where
  $m$ is the initial metric value, $m_{\mathrm{min}}$ and $m_{\mathrm{max}}$
  are the minimal and maximal values among all architectures. The RGB hexadecimal color code of the cell
  is \texttt{\#99XX99}, where X=\texttt{round}(F-6m') (\texttt{round} rounds a number to the nearest integer). \closednote{Tristan}{Use 6. Round to the nearest integer.}{Tristan}{Fixed.}}
\label{table:evaluation}
\end{table*}

@@

\paragraph{Robustness} The two workflow services are specific to
workflow execution (\texttt{R$_1$=2}). Interactions \texttt{b}
(counted twice), \texttt{c$_2$} (twice) and \texttt{d} (twice) also
are (\texttt{R$_2$=6}).
\closednote{Marc-e}{I understand both points. However, complexity is
  addressed in Robustness as well... I liked the idea of development effort. It's a tough call.}{Tristan}{Maybe 'integration challenge' is a good compromise.}

@@

                                    & \cellcolor[HTML]{99D299}{0.44}

@@

  Extensibility (normalized total)  & \cellcolor[HTML]{99D299}{0.44}
                                     & \cellcolor[HTML]{99D299}{0.44}

@@

                                     & \cellcolor[HTML]{99FF99}{0.00}\\
                                    & \cellcolor[HTML]{99E799}\textbf{2.1}

@@

                                    & \cellcolor[HTML]{99EF99}\textbf{1.9}
